\thesistitle

### 2019-05-03 sections/research.tex
Some stuff about type 1 clones

\section{Type 1 clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type.

This could invalidate a refactoring opportunity for such a code fragment. Because of that, we recommend redefining type-1 clones for refactoring. We propose to:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{Considering types:} The definition of type 2 clones states that types should not be considered. We disagree because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones, any identifiers would not be taken into account. We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables. For instance, if we call a method like this: \textit{``myMethod(var1, var2)''}, or call this method like this: \textit{``myMethod(var1, var1)''}. Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account. We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter. However, we would argue that thresholds matter here. How many literals may differ for the segment still to be considered a clone with another segment? We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary. However, because of this, completely different methods can be called in cloned fragments as a result. This poses serious challenges on refactoring and makes it more disputable whether such a clone is actually harmful. This is because different method identifiers can describe a completely different functionality. Because of that, we recommend to keep considering the call signatures of cloned methods when they are compared. We can allow variability in the rest of method identifiers by passing the function as a parameter. To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.
\end{itemize}

@@

\chapter{Clone Detection}
As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones. Many tools have been proposed to detect various types of code clones. Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. We have considered a set of these tools. However, most of these tools have a vastly different purpose than this thesis. Most of the tools are focussed on efficiency and detecting all of the types of clones. Efficiency is lesser of a concern to us, correctness is the most important aspect.

>>>>

\section{Type 1 clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments. However, when two clone fragments are textually identical, does not yet indicate that they are actually identical. Even when textually equal, method calls can refer to different methods, type declarations can refer to different types and even variables can be of a different type. See figure \ref{fig:type1noclone} for an example of a type 1 clone that is not actually identical. In this figure, you can see how all objects in the supposedly cloned fragment (see the marked fragment) refer to different imports. Because of this, it seems like a clone, but might actually not be. Even the showImage method might refer to a different method (overloaded variants). Many (mainly textual and token-based) clone detectors will flag this as a type 1 clone.

\begin{figure}[H]
	\includegraphics[width=1\textwidth]{img/type-1-no-clone}
	\caption{The marked fragment might seem like a 100\% equal clone, but actually they vary.}
	\label{fig:type1noclone}
\end{figure}

The problem with the clone shown in \ref{fig:type1noclone} is that this could invalidate a refactoring opportunity for such a code fragment (especially when we automate it). Because of that, we recommend redefining type-1 clones for refactoring. We propose to:
\begin{itemize}
  \item \textbf{Compare the equality of the fully qualified method signature for method references.} This way we can validate whether two method references, like method calls, are actually equal. In the method signature, not only the fully qualified identifier of the method should be considered, but also of the type of all its arguments. This way we can be sure that two potentially cloned method references do not point to overloaded variants (in a case that the data type of arguments is overloaded).
  \item \textbf{Compare the equality of the fully qualified identifier for type references.} This way we can be sure that two referenced types are actually equal, and that they are not just two types with the same name.
  \item \textbf{Compare the equality the fully qualified identifier for variable usages.} Two cloned lines might use a variable with the same name, but different types. This might pose serious challenges on refactoring, as the variables might not concern the same object or primitive. To check this, we need to track the declaration of variables and from this infer the fully qualified identifier of its type.
\end{itemize}

@@

\begin{itemize}
  \item \textbf{Considering types:} The definition of type 2 clones states that types should not be considered. We disagree because types can make a significant change to the meaning of a code segment and thus whether this segment should be considered a clone.
  \item \textbf{Having a distinction between different variables:} By the definition of type 2 clones, any identifiers would not be taken into account. We agree that a difference in identifiers may still result in a harmful clone, but we should still consider the distinction between different variables. For instance, if we call a method like this: \textit{``myMethod(var1, var2)''}, or call this method like this: \textit{``myMethod(var1, var1)''}. Even if the variables have the same type, the distinction between the variables is important to ensure the functionality is the same after merging.
  \item \textbf{Defining a threshold for variability in literals:} By the definition of type 2 clones any literals would not be taken into account. We agree, as when merging the clone (for instance by extracting a method), we can simply turn the literal into a method parameter. However, we would argue that thresholds matter here. How many literals may differ for the segment still to be considered a clone with another segment? We need to define a threshold to be sure that, by merging, we are not replacing a code fragment by a worse maintainable design.
  \item \textbf{Consider method call signatures and define a threshold for variability in method calls:} As type-2 clones allow changes in identifiers, also the names of called methods may vary. However, because of this, completely different methods can be called in cloned fragments as a result. This poses serious challenges on refactoring and makes it more disputable whether such a clone is actually harmful. This is because different method identifiers can describe a completely different functionality. Because of that, we recommend to keep considering the call signatures of cloned methods when they are compared. We can allow variability in the rest of method identifiers by passing the function as a parameter. To limit the amount of parameters required we also recommend defining a threshold for variability in method call expressions, so only a limited number of method calls can vary.

@@

\chapter{Clone Detection}
In this chapter, we look into the current state of clone detection research. We held a survey in which we looked into a set of clone detection tools to determine their applicability for automated refactoring. We then proposed our own tool, CloneRefactor, to be able to detect our definitions of clone types (as defined in the previous chapter).

\section{Clone detection survey}
At the beginning of this study, we set out to find a clone detection tool that we could extend to apply automated refactorings. Many tools have been proposed to detect various types of code clones. Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. We have considered a set of these tools, including some more recent ones found by a Google search. However, most of these tools have a vastly different purpose than this thesis. Most of the tools are focussed on efficiency and detecting all of the types of clones. Efficiency is lesser of a concern to us, correctness is the most important aspect.
There are a lot of clone detection tools that focus on a large amounts of
